Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.

### 2021-06-22 manuscript/article.Rmd
some nice progress

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_CBvar.RDS"))
ss_novar <- ss_sim_data[1,]
p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
                ss_novar$CB_var_gmax_s,
                ss_novar$CB_var_h_s,
                ss_novar$SB_var_gmax_s,
                ss_novar$SB_var_h_s,
                ss_novar$PB_var_gmax_s,
                ss_novar$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

@@

## Figure: Stable states with variation and tradeoff

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
ss_var <- ss_sim_data[20,]
p2  <- plot_ss_result1(ss_var$ss_res[[1]],
                ss_var$CB_var_gmax_s,
                ss_var$CB_var_h_s,
                ss_var$SB_var_gmax_s,
                ss_var$SB_var_h_s,
                ss_var$PB_var_gmax_s,
                ss_var$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}

#ss_result1 <- ss_novar$ss_res[[1]]
#ss_result2 <- ss_var$ss_res[[1]]

p_overlay <- plot_ss_result2(ss_novar$ss_res[[1]],
                             ss_var$ss_res[[1]],
                             xlims = c(-7, -1))

@@

@@

ss_sim_data <- ss_sim_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results <- unnest(ss_sim_data, cols = c(stability_measures))

results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = CB_var_gmax_s, y = hyst_range)) +
  geom_point()

>>>>

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
CBSBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))
result_index1 <- 1
p1  <- plot_ss_result1(CBSBPB_data,
                result_index = result_index1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

@@

## Figure: CBSBPB Stable states with variation and tradeoff

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
result_index2 <- 2
p2  <- plot_ss_result1(CBSBPB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}
p_overlay <- plot_ss_result2(CBSBPB_data[result_index1,]$ss_res[[1]],
                             CBSBPB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay
```

## Figure: CB Stable states with variation and tradeoff

```{r CB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
CB_data <- readRDS(here("simulations/sim data/ss_res_grad_CB_var.RDS"))
p3  <- plot_ss_result1(CB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p3
```

```{r CB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
                             CB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay
```

## Figure: SB Stable states with variation and tradeoff

```{r SB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
SB_data <- readRDS(here("simulations/sim data/ss_res_grad_SB_var.RDS"))
p4  <- plot_ss_result1(SB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p4

```{r SB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
                             SB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))

@@

## Figure: PB Stable states with variation and tradeoff

```{r PB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
PB_data <- readRDS(here("simulations/sim data/ss_res_grad_PB_var.RDS"))
p5  <- plot_ss_result1(PB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p5

```{r PB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
                             PB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))

## Figure: PB Stable states with variation and tradeoff

```{r SBPB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
SBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_SBPB_var.RDS"))
p6  <- plot_ss_result1(SBPB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p6

```{r SBPB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
                             SBPB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))

@@

CBSBPB_stab_data <- CBSBPB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results1 <- unnest(CBSBPB_stab_data, cols = c(stability_measures)) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

CB_stab_data <- CB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results2 <- unnest(CB_stab_data, cols = c(stability_measures))  %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SB_stab_data <- SB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results3 <- unnest(SB_stab_data, cols = c(stability_measures))  %>%
  mutate(var_treat = "SB",
         var_gmax = SB_var_gmax_s)

PB_stab_data <- PB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results4 <- unnest(PB_stab_data, cols = c(stability_measures))  %>%
  mutate(var_treat = "PB",
         var_gmax = PB_var_gmax_s)

SBPB_stab_data <- SBPB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results5 <- unnest(SBPB_stab_data, cols = c(stability_measures))  %>%
  mutate(var_treat = "SBPB",
         var_gmax = SB_var_gmax_s)

all_stab_results <- results1 %>%
  bind_rows(results2) %>%
  bind_rows(results3) %>%
  bind_rows(results4) %>%
  bind_rows(results5)

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat)) +
  geom_jitter()

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat)
